---
title: "Package Usage"
author: "Alex Gold"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
%\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
  ---
  
  ```{r setup, include = FALSE}
knitr::opts_chunk$set(
collapse = TRUE,
comment = "#>"
)
```

```{r}
pdf_text <- here::here("data",
                       "USSC_Public_Release_Codebook_FY99_FY16.pdf")
pdf <- pdf_load(pdf_text)
tab <- extract_tab_pages(pdf, seq(7, 57))

# Single page examples

tab_p <- tab_page(tab$text[[1]])
tab_p <- suggest_cols(tab_p)
tab_p <- suggest_rows(tab_p)
tab_p



# Example single page
tab2 <- purrr::map(tab1, function(t) {
  blanks <- get_page_blanks(t)
  t1 <- split_cols(t, blanks, TRUE)
  new_rows <- get_new_rows(t1)
  purrr::map(t1, function(x) split_rows(x, new_rows) %>% bind_cols())
})


```

```{r}
pdf <- pdf()
```


Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

output: 
rmarkdown::html_vignette:
css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

output:
rmarkdown::html_vignette:
fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
