---
title: "Package Usage"
author: "Alex Gold"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r}
# library(pdf2tab)
library(dplyr)
```

```{r}
 p <- sentencing_pdf %>%
  pdf_load() %>%
  keep_pages(7) %>%
  drop_lines(1, "top") %>%
  drop_lines(2, "bottom")
p
```

For a single-page table, it can be easy to select the columns and rows 
interactively.
```{r}
p_c <- p %>%
  set_rows(list(c(15, 22, 40, 45))) %>%
  set_cols(list(c(15, 23, 29, 66))) 
p_c

df <- p_c %>%
  as.data.frame(header = TRUE)
df
```

You can also provide custom functions for selecting rows and columns. All functions should output a numeric (or logical that can be summed). These functions must take 2 arguments, `x` and `i`. Thinking of `i` as the row (column) number, enabling use of indices like `i-1` and `i+1`.

The function will return the rows (columns) for which the function is maximized. `x[i]` should be thought of as the whole row.
```{r}
col_search <- function(x) {
  x$x != " " + x$lag == " " + x$lead != " "
}

row_search <- function(x, lag, lead) {
   sum(x != " ") - sum(lag != " ")
}

p_c <- p %>%
  # guess_cols(col_search, 5) %>%
  guess_rows(row_search, 5, header = TRUE)
p_c

df <- p_c %>%
  as.data.frame()
```



Vignettes are long form documentation commonly included in packages. Because they are part of the distribution of the package, they need to be as compact as possible. The `html_vignette` output type provides a custom style sheet (and tweaks some options) to ensure that the resulting html is as small as possible. The `html_vignette` format:

- Never uses retina figures
- Has a smaller default figure size
- Uses a custom CSS stylesheet instead of the default Twitter Bootstrap style

## Vignette Info

Note the various macros within the `vignette` section of the metadata block above. These are required in order to instruct R how to build the vignette. Note that you should change the `title` field and the `\VignetteIndexEntry` to match the title of your vignette.

## Styles

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

## Figures

The figure sizes have been customised so that you can easily put two images side-by-side. 

```{r, fig.show='hold'}
plot(1:10)
plot(10:1)
```

You can enable figure captions by `fig_caption: yes` in YAML:

    output:
      rmarkdown::html_vignette:
        fig_caption: yes

Then you can use the chunk option `fig.cap = "Your figure caption."` in **knitr**.

## More Examples

You can write math expressions, e.g. $Y = X\beta + \epsilon$, footnotes^[A footnote here.], and tables, e.g. using `knitr::kable()`.

```{r, echo=FALSE, results='asis'}
knitr::kable(head(mtcars, 10))
```

Also a quote using `>`:

> "He who gives up [code] safety for [code] speed deserves neither."
([via](https://twitter.com/hadleywickham/status/504368538874703872))
